# Chapter 5 - 

## R package: `webexercises`

Some people are using external R packages like `webexercises`, they will just work out of the box. You load it like this, I've added an extra function to attach accessibility aria labels to the entry boxes later.

```{r}
#| echo: fenced
library(webexercises)

# To allow injection of aria-labels
in_labelled_fitb <- function(answer, label_text, ...) {
  html <- webexercises::fitb(answer, ...)
  # Insert aria-label into the <input ...> tag
  html <- sub(
    "<input ",
    paste0("<input aria-label=\"", label_text, "\" "),
    html
  )
  html
}
```

The `webexercises` package also comes with a css and js file, so you typically need to add the following to the `_metadata.yml` in the folder for the file being rendered (or in the global `_quarto.yml`) if you want it literally everywhere.
```
format:
  html:
    css:
      - include/webex.css
    include-after-body: include/webex.js
```

Here's an example someone may recognise.

:::{.Example}

Consider a function taking arguments `a`, `b` and `c` and returning $(a+2\times b)^c$, defined as set out below.

```{r}
func <-  function(a, b = 0, c = 1){
    (a + 2 * b)^c
}
```

Rewrite the calls below into named form (i.e. using `parameter = value`) and give the output of `func` without running it in R.

```{r, eval=FALSE}
func(1, 2, 3)
```

This is the equivalent to `r in_labelled_fitb(
  c("func(a=1,b=2,c=3)",
    "func(a=1,c=3,b=2)",
    "func(b=2,a=1,c=3)",
    "func(b=2,c=3,a=1)",
    "func(c=3,a=1,b=2)",
    "func(c=3,b=2,a=1)"),
  label_text = "fill in the equivalent function call"
)` 
and it returns the value 
`r in_labelled_fitb("125", label_text = "fill in the return value")`.
:::
